From physical principles to ???

### 2016-05-11 2015CompleteDerivation/completeDerivation.tex
Reviewed integration that now uses the math theorems in appendix

\begin{defn}\label{integration}
	Let $\mathcal{S}$ be the state space for the particles of a homogeneous classical material. Let each state $\mathcal{s} \in \mathcal{S}$ be fully identified by a finite number of independent state variables. Then $\mathcal{S}$ is endowed with a Borel measure $\mu$. The state space $\mathcal{C}$ is isomorphic to the space of continuous functions that are integrable over any subset of $\mathcal{S}$. That is: $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$.
\end{defn}

@@

	We claim that at each $\mathcal{s} \in \mathcal{S}$ there exists a neighborhood $U \subseteq \mathcal{S}$ endowed with a Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. Each $\mathcal{s} \in \mathcal{S}$ is identified by a finite number of independent state variables. $\mathcal{S}$ is a manifold. $\mathcal{S}$ is locally compact. At each point there exists a compact neighborhood $U$. $U$ with the subspace topology is a compact Hausdorff topological space on which is defined a positive linear functional $\Lambda_U$ on the linear vector space $\mathcal{C}$ isomorphic to the space of continuous real valued functions defined on $U$. For the Riesz representation theorem for linear functionals, there exists a unique Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. As $\rho_{\mathcal{c}}$ is continuous $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{\mathrm{int}(U)} \rho_{\mathcal{c}} d \mu_U$ which is consistent with $\Lambda_U = \Lambda_{\mathrm{int}(U)}$.

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$. Let $U \subseteq V \subseteq \mathcal{S}$ two compact subsets. We have $\Lambda_V (\mathcal{c}) = \int_V \rho_{\mathcal{c}} d \mu_V = \int_U \rho_{\mathcal{c}} d \mu_V + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$. We also have $\Lambda_V (\mathcal{c}) = \Lambda_U (\mathcal{c}) + \Lambda_{V\backslash U} (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{V \backslash U} \rho_{\mathcal{c}} d \mu_{\overline{V \backslash U}} $. As the two have to be equal for all $U, V, \rho_{\mathcal{c}}$, we must have $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{U} \rho_{\mathcal{c}} d \mu_V$. Therefore $d\mu$ is unique and does not depend on the choice of neighborhood. Let $\{U_\alpha\}_{\alpha \in A}$ a cover of $\mathcal{S}$ where each $U_\alpha$ is compact. This is possible as $\mathcal{S}$ is locally compact. We have
\begin{align*}
	\Lambda_{\mathcal{S}}(\mathcal{c}) &= \sum \limits_{\alpha \in A} \Lambda_{U_\alpha}(\mathcal{c}) - \sum \limits_{\alpha \in A} \sum \limits_{\beta \in A}^{\beta \neq\alpha} \Lambda_{U_\alpha \cap U_\beta}(\mathcal{c}) \\
	&= \sum \limits_{\alpha \in A} \int_{U_\alpha} \rho_{\mathcal{c}} d\mu - \sum \limits_{\alpha \in A} \sum \limits_{\beta \in A}^{\beta \neq\alpha} \int_{U_\alpha \cap U_\beta}(\mathcal{c}) \rho_{\mathcal{c}} d\mu \\
	 &= \int_{\mathcal{S}} \rho_{\mathcal{c}} d\mu
\end{align*}
	as $\Lambda_U$ is always finite. The measure is unique on the whole space.

	We claim $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$. As per \ref{classical_vector space} $\mathcal{C}$, is isomorphic to a subspace $G \subseteq C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. As $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$, then $G \subseteq L^1_{ew}(\mathcal{S}, \mu)$. $G \subseteq C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$. Let $\rho_\mathcal{c}$ be the distribution associated with the state $\mathcal{c}$. Let $\rho \in C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ be a continuous function everywhere integral. If $\rho_\mathcal{c} \neq \rho$ then $\exists U \in \mathcal{S} | \int_{U} \rho_\mathcal{c} d \mu \neq \int_{U} \rho d \mu$. There exist an outcome in $\mathcal{S}$ that can physically distinguish the two distributions. There must be a state $\mathcal{c}_1 \in \mathcal{C} \; | \; \varrho_(\mathcal{c}_1)=\rho$. $\varrho : \mathcal{C} \rightarrow C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ is surjective. $\varrho$ is an isomorphism between $\mathcal{C}$ and $C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ as vector spaces.
\end{justification}

As we identified $C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ as the set of distributions that are physically meaningful, it's useful to show how commonly used functions spaces do not fit the bill. We do this briefly by finding counterexample. The set of continuous functions $C(\mathcal{S})$ would include functions that diverge at infinity. The set of continuous functions with compact support $C_C(\mathcal{S})$ would exclude Gaussians. The set of continuous functions that vanish at infinity $C_0(\mathcal{S})$ includes function whose integral is infinite. Schwartz space $S(\mathcal{S})$ requires functions to be infinitely smooth and we do not see a physical requirement for that.

Before we can properly identify $d\mu$, it turns out that we need to better characterize $\mathcal{S}$.

>>>>

\begin{defn}\label{integration}
	Let $\mathcal{S}$ be the state space for the particles of a homogeneous classical material. Let each state $\mathcal{s} \in \mathcal{S}$ be fully identified by a finite number of independent state variables. Then $\mathcal{S}$ is endowed with a Borel measure $\mu$. The state space $\mathcal{C}$ is isomorphic to the space of continuous functions that are integrable over any subset of $\mathcal{S}$. That is: $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ where $L^1(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \; \int_{\mathcal{S}} |\rho| d\mu < \infty \}$.
\end{defn}

@@

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$.  Each $\mathcal{s} \in \mathcal{S}$ is identified by a finite number of independent state variables. $\mathcal{S}$ is a manifold. $\mathcal{S}$ is locally compact. $\mathcal{C} \cong G \subseteq C(\mathcal{S})$ therefore $\Lambda_U(\mathcal{c}) \cong \Lambda_U(\rho_\mathcal{c})$. $\Lambda = \{\Lambda_U : C(\mathcal{S}) \rightarrow \mathbbm{R}\}_{U \subseteq \mathcal{S}}$ is a family of positive linear functionals such that $\forall U \subseteq \mathcal{S} \; \Lambda_U = \Lambda_{\mathrm{int}(U)}$ and $\Lambda_{U_1} + \Lambda_{U_2} = \Lambda_{U_1 \cup U_2} + \Lambda_{U_1 \cap U_2} \; \forall U_1, U_2 \subseteq \mathcal{S}$. For the extension \ref{extended_riesz_theorem} of the Riesz representation theorem for linear functionals 
	there exists a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_{U} \rho_\mathcal{c} d\mu$.

	We claim $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$. As per \ref{classical_vector space} $\mathcal{C}$, is isomorphic to a subspace $G \subseteq C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. As $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$, then $G \subseteq \{ \rho : S \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq S\} = L^1(\mathcal{S}, \mu)$ for \ref{everywhere_integrable_is_lebesgue_integrable}.  $G \subseteq C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$. Let $\rho_\mathcal{c}$ be the distribution associated with the state $\mathcal{c}$. Let $\rho \in C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ be a continuous function everywhere integral. If $\rho_\mathcal{c} \neq \rho$ then $\exists U \in \mathcal{S} | \int_{U} \rho_\mathcal{c} d \mu \neq \int_{U} \rho d \mu$. There exist an outcome in $\mathcal{S}$ that can physically distinguish the two distributions. There must be a state $\mathcal{c}_1 \in \mathcal{C} \; | \; \varrho_(\mathcal{c}_1)=\rho$. $\varrho : \mathcal{C} \rightarrow C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ is surjective. $\varrho$ is an isomorphism between $\mathcal{C}$ and $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as vector spaces.
\end{justification}

As we identified $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as the set of distributions that are physically meaningful, it's useful to briefly show how other commonly used functions spaces do not fit the bill. The set of continuous functions $C(\mathcal{S})$ would include functions that diverge at infinity. The set of continuous functions with compact support $C_C(\mathcal{S})$ would exclude Gaussians. The set of continuous functions that vanish at infinity $C_0(\mathcal{S})$ includes function whose integral is infinite. Schwartz space $S(\mathcal{S})$ excludes functions that are not infinitely smooth which we don't have a physical argument for. The set of Lebesgue integrable functions $L^1(\mathcal{S})$ includes discontinuous functions that for \ref{continuous_map} are unphysical.

Another point is that while the norm associated to $L^1(\mathcal{S})$ is $\int_{\mathcal{S}} |\rho| d\mu$, the pseudo-norm $\int_{\mathcal{S}} \rho d\mu$ is perhaps more physically meaningful. For proper states, the two are the same and they represent the total amount of material. For state changes they differ. The second represents the amount of material added (or taken away if negative) by the state change. For example, if $\rho_{\delta \mathcal{c}}$ is the change due to deterministic and reversible evolution, the amount of material does not change and therefore $\int_{\mathcal{S}} \rho_{\delta \mathcal{c}} d\mu = 0$. The first norm would represent the total amount of material that is changing (i.e. being added and being removed), therefore $\int_{\mathcal{S}} |\rho_{\delta \mathcal{c}}| d\mu = 0$ means no material is moving, no change is occurring.

We now turn our attention to the metric $d\mu$ which we need to properly identify. It turns out that before we can do it, we need to better characterize $\mathcal{S}$.
